ECE498:~Senior Capstone Project I\\\textbf{\underline{Project Proposal}}\\ \vspace{0.5in} Project Title: Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle \vspace{1.0in} \author{Hannah Grady and Nicholas Nauman\\ Advisor: Dr.~Suruz Miah}

### 2021-10-31 proposal.tex
Updated Proposal.tex file
I added my summary of a MATLAB tutorial and also started working on the parts list and timeline sections.

\subsection{Example 1: ..........}
\label{sec:sysID-Example1}

@@

% % \section{Parts List}

% \section{Timeline and Milestones} \label{sec:timeline}

% \begin{figure}
%   \centering
%   \begin{ganttchart}[
%     hgrid,
%     vgrid,
%     x unit=.6cm,
%     y unit title=.8cm,
%     y unit chart=.6cm,
%     milestone label font=\tiny,
%     milestone progress label font = \tiny,
%     milestone progress label anchor = east,
%     bar label font=\tiny,
%     group label font=\small,
%     bar/.append style={fill=green},
%     bar incomplete/.append style={fill=red},
%     group progress label font = \tiny,
%     progress label text={$\displaystyle#1\%$},
%     group progress label anchor = east,
%     bar progress label font = \tiny,
%     bar progress label anchor = east,
%     ]{1}{17}

%     \gantttitle{2020}{17}\\
%     \gantttitle{Sep}{4}
%     \gantttitle{Oct}{4}
%     \gantttitle{Nov}{4}
%     \gantttitle{Dec}{4}
%     \gantttitle{}{1}\\

%     \ganttgroup[progress = 100]{Research}{3}{12} \\
%     \ganttbar[progress = 100]{Research Multipath}{3}{12}\\
%     \ganttbar[progress = 100]{Research Reflector}{3}{12}\\

%     \ganttgroup[progress = 80]{Simulation}{8}{10}\\
%     \ganttbar[progress = 80]{CoppeliaSim simulation}{8}{10}\\
%     \ganttmilestone[progress = 0]{Simulation Complete}{10}\\

%     \ganttgroup[progress = 100]{Project Proposal}{11}{12}\\
%     \ganttbar[progress = 100]{Proposal Document}{11}{11}\\
%     \ganttbar[progress = 100]{Proposal Presentation}{12}{12}\\

%     \ganttgroup[progress = 82.5]{XBee Setup}{13}{14}\\
%     \ganttbar[progress = 90]{Voltage Regulator Circuit}{13}{13}\\
%     \ganttbar[progress = 80]{Configuration with X-CTU}{14}{14}\\
%     \ganttbar[progress = 90]{Sensing RSSI}{14}{14}\\
%     \ganttbar[progress = 70]{Serial Communication}{14}{14}\\
%   \end{ganttchart}
% \caption{Gantt chart for Fall 2020}
% \label{fig:gantt1}
% \end{figure}

% \begin{figure}
%   \centering
%   \begin{ganttchart}[
%     hgrid,
%     vgrid,
%     x unit=.6cm,
%     y unit title=.8cm,
%     y unit chart=.6cm,
%     milestone label font=\tiny,
%     milestone progress label font = \tiny,
%     milestone progress label anchor = east,
%     bar label font=\tiny,
%     group label font=\small,
%     bar/.append style={fill=green},
%     bar incomplete/.append style={fill=red},
%     group progress label font = \tiny,
%     progress label text={$\displaystyle#1\%$},
%     group progress label anchor = east,
%     bar progress label font = \tiny,
%     bar progress label anchor = east,
%     ]{1}{18}
%     \gantttitle{2021}{18}\\
%     \gantttitle{Jan}{2}
%     \gantttitle{Feb}{4}
%     \gantttitle{Mar}{4}
%     \gantttitle{Apr}{4}
%     \gantttitle{May}{4}\\

%     \ganttgroup[progress = 0]{Assembly}{3}{4}\\
%     \ganttbar[progress = 0]{Replace Motors}{3}{3}\\
%     \ganttbar[progress = 0]{Design and Construct Reflector}{3}{4}\\
%     \ganttbar[progress = 0]{Mount Reflector}{4}{4}\\
%     \ganttmilestone[progress = 0]{Assembly Complete}{4}\\

%     \ganttgroup[progress = 10]{Software}{5}{6}\\
%     \ganttbar[progress = 20]{XBee Library}{5}{5}\\
%     \ganttbar[progress = 0]{Control Library}{6}{6}\\

%     \ganttgroup[progress = 0]{Angle Estimation}{7}{8}\\
%     \ganttbar[progress = 0]{Rotate XBee on Stepper Motor}{7}{7}\\
%     \ganttbar[progress = 0]{Determine Angle}{8}{8}\\

%     \ganttgroup[progress = 0]{Distance Estimation}{9}{10}\\
%     \ganttbar[progress = 0]{Calibrate Distance Calculation}{9}{10}\\

%     \ganttgroup[progress = 0]{Subsystem Integration}{11}{15}\\
%     \ganttbar[progress = 0]{Angle Estimation Testing}{11}{11}\\
%     \ganttbar[progress = 0]{Distance Estimation Testing}{12}{13}\\
%     \ganttbar[progress = 0]{System Testing}{14}{15}\\
%     \ganttmilestone[progress = 0]{Integration Complete}{15}\\

%     \ganttgroup[progress = 0]{Project Completion}{16}{17}\\
%     \ganttbar[progress = 0]{Final Report}{16}{16}\\
%     \ganttbar[progress = 0]{Final Presentation}{17}{17}\\
%     \ganttbar[progress = 0]{Presentation to IAB}{17}{17}\\
%     \ganttbar[progress = 0]{Project Demo}{17}{17}\\

%     \ganttmilestone[progress = 0]{Project Complete}{17}
%   \end{ganttchart}
%   \caption{Gantt Chart for Spring 2020}
%   \label{fig:gantt2}
% \end{figure}

>>>>

\subsection{Example 1: Dealing with Multi-Variable Systems: Identification and Analysis}
\label{sec:sysID-Example1}
During this example I learned how to create an iddata object from a dataset in order to get the inputs and the outputs. The next step was to look at the impulse and step responses in order to learn more about how the inputs and outputs act. From there the state space model was estimated using the first part of the given data. This model was compared to the step responses that were found earlier and with the second part of the data to see if it was a good fit. The model had a best fit percentage of 83.55\% for the generated voltage data, and a best fit of 39.33\% for the speed data. The frequency response of the model was estimated with spectral analysis and bode plots were also created. The tutorial explained that if the data doesn’t give nice models, then it is best to try out submodels for the different channels. Two single-input single-output (SISO) models were created and compared with the existing multiple-input multiple-output (MIMO) model and the actual data. The Nyquist plots were also compared. Both SISO models performed well during these comparisons. The next step in the tutorial was to create a multiple-input single-output (MISO) model in order to get a model that more accurately reflected the generated voltage data. By creating this model and comparing it to the validation data and previous models, we saw a best fit percentage of 90.18\%. The last thing the example showed was how to merge the two SISO models we created earlier.

@@

\section{Parts List}
	\subsection{Software}
	\begin{itemize}
    \item MATLAB's System Identification Toolbox 
    \item  
 \end{itemize}

	\subsection{Hardware} 
	\begin{itemize}
    \item Laptop
    \item PAC Mod 
    \item CAN Case 
    \item CAN Bus 
 \end{itemize}

\section{Timeline and Milestones} \label{sec:timeline}

 \begin{figure}
   \centering
   \begin{ganttchart}[
     hgrid,
     vgrid,
     x unit=.6cm,
     y unit title=.8cm,
     y unit chart=.6cm,
     milestone label font=\tiny,
     milestone progress label font = \tiny,
     milestone progress label anchor = east,
     bar label font=\tiny,
     group label font=\small,
     bar/.append style={fill=green},
     bar incomplete/.append style={fill=red},
     group progress label font = \tiny,
     progress label text={$\displaystyle#1\%$},
     group progress label anchor = east,
     bar progress label font = \tiny,
     bar progress label anchor = east,
     ]{1}{17}

%     \gantttitle{2020}{17}\\
     \gantttitle{Sep}{4}
     \gantttitle{Oct}{4}
     \gantttitle{Nov}{4}
     \gantttitle{Dec}{4}
     \gantttitle{}{1}\\

%     \ganttgroup[progress = 100]{Research}{3}{12} \\
     \ganttbar[progress = 100]{Read System Identification Documentation}{3}{12}\\
     \ganttbar[progress = 100]{Collect Steering, Acceleration, and Braking Data}{3}{12}\\

%     \ganttgroup[progress = 80]{Simulation}{8}{10}\\
     \ganttbar[progress = 80]{System Identification Tutorials}{8}{10}\\
     \ganttbar[progress = 100]{System Functional Requirements Document}{8}{10}\\
          \ganttbar[progress = 100]{System Functional Requirements Presentation}{8}{10}\\

     \ganttbar[progress = 100]{Parts Order Request}{8}{12}\\
     \ganttbar[progress = 100]{Proposal Document}{11}{11}\\
     \ganttbar[progress = 100]{Proposal Presentation}{12}{12}\\

%     \ganttgroup[progress = 82.5]{XBee Setup}{13}{14}\\
     \ganttmilestone[progress = 90]{Model Steering System}{13}{13}\\
     \ganttbar[progress = 80]{Model Acceleration System}{14}{14}\\
     \ganttbar[progress = 90]{Model Braking System}{14}{14}\\

   \end{ganttchart}
 \caption{Gantt chart for Fall 2021}
 \label{fig:gantt1}
 \end{figure}

 \begin{figure}
   \centering
   \begin{ganttchart}[
     hgrid,
     vgrid,
     x unit=.6cm,
     y unit title=.8cm,
     y unit chart=.6cm,
     milestone label font=\tiny,
     milestone progress label font = \tiny,
     milestone progress label anchor = east,
     bar label font=\tiny,
     group label font=\small,
     bar/.append style={fill=green},
     bar incomplete/.append style={fill=red},
     group progress label font = \tiny,
     progress label text={$\displaystyle#1\%$},
     group progress label anchor = east,
     bar progress label font = \tiny,
     bar progress label anchor = east,
     ]{1}{18}
     %\gantttitle{2021}{18}\\
     \gantttitle{Jan}{2}
     \gantttitle{Feb}{4}
     \gantttitle{Mar}{4}
     \gantttitle{Apr}{4}
     \gantttitle{May}{4}\\

%     \ganttgroup[progress = 0]{Assembly}{3}{4}\\
     \ganttbar[progress = 0]{Collect Shift, Speed Control, and Speed Data}{3}{3}\\
     \ganttbar[progress = 0]{Model Shift System}{3}{4}\\
     \ganttbar[progress = 0]{Model Speed Control System}{4}{4}\\
     \ganttbar[progress = 0]{Model Speed System}{4}{10}\\

%     \ganttgroup[progress = 10]{Software}{5}{6}\\
     \ganttbar[progress = 20]{Test Subsystems}{5}{5}\\
     \ganttmilestone[progress = 0]{Test Subsystems with HIL}{6}{6}\\

%     \ganttgroup[progress = 0]{Project Completion}{16}{17}\\
     \ganttmilestone[progress = 0]{Final Report}{16}{16}\\
     \ganttmilestone[progress = 0]{Final Presentation}{17}{17}\\
     \ganttbar[progress = 0]{Presentation to IAB}{17}{17}\\
     \ganttbar[progress = 0]{Project Demo}{17}{17}\\

%     \ganttmilestone[progress = 0]{Project Complete}{17}
   \end{ganttchart}
   \caption{Gantt Chart for Spring 2022}
   \label{fig:gantt2}
 \end{figure}
